### 2021-04-21 written/eLifeRevision/Bittner_eLife2020.tex
additional SC supp fig

@@

\subsubsection{Optogenetic silencing modeling} \label{methods_sc_opto}
We tested whether the inferred SC model connectivities could reproduce experimental effects of optogenetic inactivation in rats \cite{duan2015requirement}.
During periods of simulated optogenetic inactivation, activity was decreased proportional to the optogenetic strength $\gamma$
\begin{equation}
x_\alpha = (1-\gamma)\phi(u_\alpha).
\end{equation}
Delay period inactivation was from $0.8 < t < 1.2$.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.8]{figures/figSC8/figSC8.pdf}
\end{center}
\caption{\small (SC8): 
\textbf{A}. Entropy throughout optimization. 
\textbf{B}. The emergent property statistic means and variances converge to their constraints at 20,000 iterations following the tenth augmented Lagrangian epoch.
}
\label{fig:SC8}
\end{figure}

The bend in the EPI distribution is not a spurious result of the EPI optimization.
The structure discovered by EPI matches the shape of the set of points returned from brute-force random sampling (Fig. \ref{fig:SC8}A) 
These connectivities were sampled from a uniform distribution over the range of each connectivity parameter, and all parameters producing accuracy in each task within the range of 60\% to 90\% were kept.
This set of connectivities will not match the distribution of EPI exactly, since it is not conditioned on the emergent property.
For example the parameter set returned by the brute-force search is biased towards lower accuraciess (Fig. \ref{fig:SC8}B).

@@

\subsubsection{Modeling optogenetic silencing.} \label{methods_sc_opto}
We tested whether the inferred SC model connectivities could reproduce experimental effects of optogenetic inactivation in rats \cite{duan2015requirement}.
During periods of simulated optogenetic inactivation, activity was decreased proportional to the optogenetic strength $\gamma$
\begin{equation}
x_\alpha = (1-\gamma)\phi(u_\alpha).
\end{equation}
Delay period inactivation was from $0.8 < t < 1.2$.
